Topic and tone of political news articles in German online media.

### 2018-04-10 paper/docs/04_Modelresults_50.Rmd
typos

print(xtable(coeff_tab[1:56,], type="latex"), file="../writing/tables/coeff1.tex" )
print(xtable(coeff_tab[57:nrow(coeff_tab),], type="latex"), file="../writing/tables/coeff2.tex" )
```

@@

p1 <- ggplot(p, 
       aes(yearmonth, sentiment_w, 
           group = topic_name,
           label = obs)) +
  facet_wrap(~topic_name, nrow = 3, labeller=labeller(topic_name = linebreak)) +
  geom_col(fill = col[3], alpha = 0.8) +
 geom_line(color = col[5], size = 0.6) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  labs(x="", y="Sentiment Score",
        title = "",
       subtitle = "") +
  scale_x_date(breaks = date_breaks("1 month"), 
               labels = date_format("%b", tz ="CET")) +
  theme(strip.text = element_text(size=14),
    axis.text.y = element_text(size=10),
        axis.text.x = element_text(size = 10, angle = 45))

ggsave(filename = "../figs/sentscore_monthly.png", plot = p1, 
       height = 10, width = 12)
```

@@

p1 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment_w, 
           group = site,
           label = obs)) +
  geom_col(fill=col[3], alpha = 0.8) +
  #geom_line(color = col[2], size = 0.8) +
  #geom_text(size = 2) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="Sentiment Score",
       title = "") +
  theme(strip.text = element_text(size = 11),
    axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size=8, angle = 90),
        axis.title.x = element_text(size = 12))

@@

```{r fig.height=6, fig.width=8}
p <- corr %>%
  filter(lag == 0) %>%
  ggplot(aes(Var2, Var1,
                 fill = correlation,
                 label = round(correlation,2))) +
        geom_tile(color="white", alpha=0.8) +
        geom_text(size = 3.5) +
        #viridis::scale_fill_viridis(limits=c(-1, 1)) +
        labs(x="", y="", fill="",
             title = "",
             subtitle = "Election polls vs. topic sentiment value (monthly)")

>>>>

print(xtable(coeff_tab[1:56,], type="latex", digits=3), 
      file="../writing/tables/coeff1.tex" )
print(xtable(coeff_tab[57:nrow(coeff_tab),], type="latex", digits=3), 
      file="../writing/tables/coeff2.tex" )
```

@@

p1 <- ggplot(p, 
       aes(yearmonth, sentiment_w, 
           group = topic_name,
           label = obs)) +
  facet_wrap(~topic_name, nrow = 3, 
             labeller=labeller(topic_name = linebreak)) +
  geom_col(fill = col[3], alpha = 0.8) +
 geom_line(color = col[5], size = 0.6) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  labs(x="", y="Sentiment Score",
        title = "",
       subtitle = "") +
  scale_x_date(breaks = date_breaks("1 month"), 
               labels = date_format("%b-%y", tz ="CET")) +
  theme(strip.text = element_text(size=14),
    axis.text.y = element_text(size=10),
    axis.title.y = element_text(size=12),
        axis.text.x = element_text(size = 12, angle = 45))

ggsave(filename = "../figs/sentscore_monthly.png", plot = p1, 
       height = 10, width = 13)
```

@@

p1 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment_w, 
           group = site,
           label = obs)) +
  geom_col(fill=col[3], alpha = 0.8) +
  #geom_line(color = col[2], size = 0.8) +
  #geom_text(size = 2) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="Sentiment Score",
       title = "") +
  theme(strip.text = element_text(size = 11),
    axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size=8, angle = 90),
        axis.title.x = element_text(size = 12))

@@

Cross correlation at lag 0
```{r}
# Table
corr %>% 
  filter(lag == 0) %>%
  select(-lag) %>% 
  spread(Var2, correlation) -> corr_tab

print(xtable(corr_tab, type="latex", digits=3,
                   caption = "Cross Correlation at lag 0"),
      file="../writing/tables/corr.tex" )
```

```{r fig.height=6, fig.width=8}
# Figure
p <- corr %>%
  filter(lag == 0) %>%
  ggplot(aes(Var2, Var1,
                 fill = correlation,
                 label = round(correlation,2))) +
        geom_tile(color="white", alpha=0.8) +
        geom_text(size = 3.5) +
        #viridis::scale_fill_viridis(limits=c(-1, 1)) +
        labs(x="", y="", fill="",
             title = "",
             subtitle = "Election polls vs. topic sentiment value (monthly)")

### 2018-04-10 paper/writing/structure.tex
typos

The sentiment analysis is conducted with those documents that are assigned to one of the above selected topics with the highest probability. A dictionary-based method is then applied on the remaining 5611 documents with the aim to measure the tone (or sentiment) of a document. The idea of a sentiment analysis is to determine the attitude of a writer toward the overall tonality of a document. To conduct such an analysis, a lists of words (dictionary) associated with a given emotion, such as negativity is pre-defined by the analyst. The document is then deconstructed into individual words and the frequencies of words contained in a given dictionary are then calculated.

Such lexical or “bag-of-words” approaches are widely presented in the finance literature to  determine  the  effect  of  central  banks’  monetary  policy  communications on asset prices and real variables (\citet{nyman_news_2018} \citep{tetlock_giving_2007}, \citep{tetlock_more_2008}). \citet{hansen_shocking_2016} use a similar approach to measure "the two Ts" (Topic and tone). They explore the effects of FOMC (Federal Open Market Committee) statements on both market and real economic variables. To understand the multi-dimensional information a statement is transmitting, they apply LDA on a corpus of 142 FOMC decision statements split into sentences (topic). They then measure how the central bank is talking about that topic, using a dictionary approach (tone). To calculate their score, they subtract the negative words from the positive words und divide this by the number of total words of the statement. A similar score is used by \citet{nyman_news_2018}, who measure the effect of narratives and sentiment of financial market text-based data on developments in the financial system. They count the number of occurrences of excitement words and anxiety words and then scale these numbers by the total text size as measured by the number of characters.

The present paper uses a dictionary that lists words associated with positive and negative polarity weighted within the interval of $[-1; 1]$. SentimentWortschatz\footnote{SentiWS for short. available here: http://wortschatz.uni-leipzig.de/de/download}, is a publicly available German-language resource for sentiment analysis, opinion mining etc. The current version of SentiWS (v1.8b) contains 1,650 positive and 1,818 negative words, which sum up to 15,649 positive and 15,632 negative word forms incl. their inflections, respectively. The sentiment score for each document $d$ is calculated  based on the weighted polarity values for a word, defined on an interval between -1 and 1. The score is then calculated from the sum of the words in a document (which can be assigned to a word from the dictionary) divided by the total number of words in that document:

@@

The following figure shows the results of the analysis for each topic on a monthly basis, aggregated on all newspapers. Each sentiment value is weighted by the relative share of the topic in the overall reporting of that month.

Some conclusions can be drawn from this illustration. First of all, it can be seen that, on average, all topics are discussed almost exclusively negatively. An exception is topic 27 concerning the Jamaica coalition negotiations, which shows a positive sentiment value for a short period of time (October 2017). In the following month (November 2017), after it became clear that there would be no coalition between the CDU/CSU/CSU, FDP and Die Grünen, the value of this topic as well as that of topic 26 drops rapidly, but then rises again in February. Concerning the issues that discuss the great coalition between CDU/CSU/CSU and SPD, it is evident that the overall tone is in which this topic is discussed is generally decreasing from November 2017 to January 2018, but in the following February, the sentiment value of this topic rises. However, the sentiment score of topics that deal with the SPD (1, 17, 22) is diminishing in the course of time, with topic 17 recording the largest decline. For the other parties the process is rather zigzag-like.

@@

If aggregated by news provider, some differences between the sites are discernible (Figure \ref{fig_sentscore_site}). To begin with, it can be noted that on average all topics are discussed negatively by all news providers, except topic 22, which mainly covers the personnel debates of the SPD and has a positive value at Tagesschau.de. One striking feature is the way in which the Jamaica negotiations and their failure are reported (topics 27 and 26). Although all providers discuss this topics in a negative light, Bild.de reports them particularly negative. The same applies to the reports on the grand coalition, where the value of ZEIT ONLINE is the most negative.

We use two different Figures to analyze the differences between the media outlets graphically: We use the bar plot to examine the polarity tendencies of the individual topics within a medium (Figure \ref{fig_sentscore_site}) and the radar plot to observe the differences between the media (Figure \ref{fig_sentscore_radar}).

Starting with the bar plot it becomes apparent that all topics are discussed negatively, except topic 23 at Tagesschau.de. At Bild.de, the topics that include the coalition negotiations (26,27,4) and the SPD (1,17) are the most negative. The topics relating to AfD (20,30,32,37) are also discussed more negatively. Looking at the values of WELT ONLINE, two of the AfD topics have the most negative value (32.20). Topic 27 concerning the Jamaica Coalition (27) and the Grand Coalition (4) also score relatively negatively. Concerning FOCUS ONLINE, it is mainly topics that relate to the SPD (27, 17, 4, 1) that have a strong negative sentiment value, together with topic 32 and 37. Turning to SPIEGEL ONLINE, it is noticeable that the difference in sentiment value between the individual topics is less pronounced. Topics 13 and 10 stand out as comparatively less negative. However, these issues are also the least negatively discussed in the other media. Also at stern.de the difference in sentiment value is less significant and overall less negative. The topics regarding CDU/CSU (46) and Martin Schulz (10) score the most positively (or least negatively). Tagesschau.de is the least negative on most topics, or even once positive. However, this does not apply to topic 23 (CSU), where tagesschau.de is most negative in comparison to the other media. As with Bild.de, the issues relating to the coalition negotiations (27 and 4) also come off rather badly with ZEIT ONLINE. However, the issues surrounding AfD (30, 32, 37 and 20) are even more negative than at Bild.de.

@@

A good overview of how differently the topics are discussed by the providers is shown in Figure \ref{fig_sentscore_radar}. It becomes evident that the sentiment value of the media differs most notably with regard to topic 27 and topic 4, i. e. the topics on which the coalition negotiations are reported. With regard to the Jamaica coalition, Bild.de reports the most and tagesschau.de the least negative. The reporting of ZEIT ONLINE concerning the grand coalition is the one with the most negative sentiment value and again Tagesschau.de, together with stern.de, the one with the value which is least negative. Furthermore, it becomes evident that the negative sentiment value of FOCUS ONLINE regarding topic 17 is high in relation to the other media. FOCUS ONLINE thus reports comparatively more negatively on the debates within the SPD. This includes in particular the vote on a possible coalition with CDU/CSU/CSU. For topic 1, which also deals with the SPD, the value of FOCUS ONLINE is rather negative, only undercut by Bild.de. Topics related to AfD do not show striking differences.

\begin{figure}[H]
	\caption{Sentiment Score by news wire}
	\begin{center}
			\includegraphics[width=0.8\textwidth,keepaspectratio]{../figs/sentscore_radar.png}
			\label{fig_sentscore_radar}
	\end{center}
\end{figure}

@@

\begin{enumerate}
	\item The sentiment value of the SPD is decreasing over time, especially in regard to internal votes. 
	\item The topics relating to the coalition talks on Jamaica (26, 27) and the grand coalition (4) are discussed rather critically, but they also show the greatest differences between the media. In contrast, the tonality of the topics in relation to the AfD shows rather small differences. 
	\item Overall, the sentiment value at Tagesschau.de is the least negative and only shows a comparatively strong negative value at topic 23, concerning the CSU.
\end{enumerate}

\subsection{News sentiment and poll data}\label{ch_correlation}
% add ccf table

@@

In the present paper, the relationship between monthly average of both the sentiment value of individual topics ($x_t$) and the survey value of the parties ($y_t$) is estimated using the cross correlation function (CCF). Thus, the CCF between $x_{t+h}$ and $y_t$ for $h\pm 1$,$h \pm 2$,$h \pm 3$ is computed. A negative value for $h$ is a correlation between the topic sentiment value at a time before $t$ and the survey value at time $t$. The correlation value for $h=0$ indicates the contemporary correlation between the two time series.  Based on the coefficients of the cross correlation estimation shown in Figure \ref{fig_ccf}, the significant correlations between topic sentiment and survey value are evaluated for each party. It is important to note that no causal relationships are described below, but that only the correlation between the two time series is described.

The survey results of the AfD correlate negatively with topics relating to the SPD (17, 22) at lag 0. Thus, if the SPD was more negatively reported, the poll value of the AfD increased in the same month (and vice versa). Another significant negative correlation exists between the reporting on the GroKo (4) and the survey value of AfD at lag -1 ($x_{t-1}$). So if the GroKo was more negatively reported in one month, the survey value of the AfD increased in the following month (and vice versa). For the FDP, too, only negative correlation coefficients can be detected, with the strongest negative correlation existing for the topic relating to the CSU (23). If the CSU got off worse in the online news, the poll value of the FDP have gone up. Another interesting observation is that the FDP's poll results correlate negatively with issues relating to the Jamaica coalition at lag 1 ($x_{t+1}$). So if the poll results for the FDP rose in one month, the following month the FDP was reported more negatively. The Green Party survey results show no negative correlation with any of the topics, except topic 30 at lag 1. It is striking that there seems to be a strong negative correlation between the SPD topics (1, 17,22) and the poll results of the left party (DIE LINKE). This means that the poll value of the left party has climbed if the topics related to the SPD were discussed more negatively. Same applies to the reporting on the GroKo (30) for lag -1. Conversely, the SPD's survey results correlate strongly positively with these topics, and also with topic 30 with a delay of one month. The CDU/CSU's survey results correlate most positively with topics relating to coalition negotiations. For the CDU/CSU, too, only significant negative correlations are discernible: the survey results correlate negatively with the topic of the Schulz v Merkel debate (10) and negatively with topic 30 with a delay of one month ($x_{t+1}$).

@@

\printbibliography
\section*{Appendix}

\subsection*{Most frequent words\label{apx_tf}
% 1, 2
\begin{figure}[H]
	\begin{center}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote1.png}
		\end{subfigure}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote2.png}
		\end{subfigure}
	\end{center}
\end{figure}

@@

\subsection*{Regression Results}\label{apx_coeff}
\todo{round estimates}
\input{tables/coeff1}
\input{tables/coeff2}

>>>>

The sentiment analysis is performed with the documents for which one of the above topics has the highest posterior probability and if this probability is greater than 30\%. A dictionary-based method is then applied on the remaining 5611 documents with the aim to measure the tone (or sentiment) of a document. The idea of a sentiment analysis is to determine the attitude of a writer toward the overall tonality of a document. To conduct such an analysis, a lists of words (dictionary) associated with a given emotion, such as negativity is pre-defined by the analyst. The document is then deconstructed into individual words and the frequencies of words contained in a given dictionary are calculated.

Such lexical or “bag-of-words” approaches are widely presented in the finance literature to determine the effect of central banks' monetary policy communications on asset prices and real variables (\citet{nyman_news_2018} \citep{tetlock_giving_2007}, \citep{tetlock_more_2008}). \citet{hansen_shocking_2016} use a similar approach to measure "the two Ts" (Topic and tone). They explore the effects of FOMC (Federal Open Market Committee) statements on both market and real economic variables. To understand the multi-dimensional information a statement is transmitting, they apply LDA on a corpus of 142 FOMC decision statements split into sentences (topic). They then measure how the central bank is talking about that topic, using a dictionary approach (tone). To calculate their score, they subtract the negative words from the positive words und divide this by the number of total words of the statement. A similar score is used by \citet{nyman_news_2018}, who measure the effect of narratives and sentiment of financial market text-based data on developments in the financial system. They count the number of occurrences of excitement words and anxiety words and then scale these numbers by the total text size as measured by the number of characters.

The present paper uses a dictionary that lists words associated with positive and negative polarity weighted within the interval of $[-1; 1]$. SentimentWortschatz\footnote{SentiWS for short. available here: http://wortschatz.uni-leipzig.de/de/download}, is a publicly available German-language resource for sentiment analysis, opinion mining etc. The current version of SentiWS (v1.8b) contains 1,650 positive and 1,818 negative words, which sum up to 15,649 positive and 15,632 negative word forms including their inflections, respectively. The sentiment score for each document $d$ is calculated  based on the weighted polarity values for a word, defined on an interval between -1 and 1. The score is then calculated from the sum of the words in a document (which can be assigned to a word from the dictionary) divided by the total number of words in that document:

@@

Figure \ref{fig_sentscore_monthly} shows the results of the analysis for each topic on a monthly basis, aggregated on all newspapers. Each sentiment value is weighted by the relative share of the topic in the overall reporting of that month.

Some conclusions can be drawn from this illustration. First of all, it can be seen that, on average, all topics are discussed almost exclusively negatively. An exception is topic 27 concerning the Jamaica coalition negotiations, which shows a positive sentiment value for a short period of time (October 2017). In the following month (November 2017), after it became clear that there would be no coalition between the CDU/CSU, FDP and Die Grünen, the value of this topic as well as that of topic 26 drops rapidly, but then rises again in February. Concerning the issues that discuss the great coalition between CDU/CSU and SPD, it is evident that the overall tone in which this topic is discussed is generally decreasing from November 2017 to January 2018, but in the following February, the sentiment value of this topic rises. However, the sentiment score of topics that deal with the SPD (1, 17, 22) is diminishing in the course of time, with topic 17 recording the largest decline. For the other parties the process is rather zigzag-like.

@@

In order to analyze the differences between the news websites, two different figures are considered: The bar plot is used to examine the polarity tendencies of the individual topics for a the respective website (Figure \ref{fig_sentscore_site}) and the radar plot is considered to observe the differences between the websites (Figure \ref{fig_sentscore_radar}).

Starting with the bar plot it becomes apparent that all topics are discussed negatively, except topic 23 at Tagesschau.de. At Bild.de, the topics that include the coalition negotiations (26, 27, 4) and the SPD (1, 17) are the most negative. The topics relating to AfD (20,30,32,37) are also discussed more negatively. Looking at the values of DIE WELT, two of the AfD topics have the most negative value (32, 20). Topic 27 concerning the Jamaica Coalition and the Grand Coalition (4) also score relatively negatively. Concerning FOCUS ONLINE, it is mainly topics that relate to the SPD (27, 17, 4, 1) that have a strong negative sentiment value, together with topic 32 and 37 - both related to AfD. Turning to SPIEGEL ONLINE, it is noticeable that the difference in sentiment value between the individual topics is less pronounced. Topics 13 (election campaign of A.Merkel) and 10 (A.Merkel vs M.Schulz) stand out as comparatively less negative. However, these issues are also the least negatively discussed in the other media. Also at stern.de the difference in sentiment value is less significant and overall less negative. The topics regarding CDU/CSU (46) and Martin Schulz (10) score the most positively (or least negatively). Tagesschau.de is the least negative on most topics, or even once positive. However, this does not apply to topic 23 (CSU), where tagesschau.de is most negative in comparison to the other media. As with Bild.de, the issues relating to the coalition negotiations (27 and 4) also come off rather badly with ZEIT ONLINE. However, the issues surrounding AfD (30, 32, 37 and 20) are even more negative than at Bild.de.

@@

A good overview of how differently the topics are discussed by the providers is shown in Figure \ref{fig_sentscore_radar}. It becomes evident that the sentiment value of the media differs most notably with regard to topic 27 and topic 4, i.e. the topics on which the coalition negotiations are reported. With regard to the Jamaica coalition, Bild.de reports the most and tagesschau.de the least negative. The reporting of ZEIT ONLINE concerning the grand coalition is the one with the most negative sentiment value and again Tagesschau.de, together with stern.de, the one with the value which is least negative. Furthermore, it becomes evident that the negative sentiment value of FOCUS ONLINE regarding topic 17 is high in relation to the other media. FOCUS ONLINE thus reports comparatively more negatively on the debates within the SPD. This includes in particular the vote on a possible coalition with CDU/CSU/CSU. For topic 1, which also deals with the SPD, the value of FOCUS ONLINE is rather negative, only undercut by Bild.de. Topics related to AfD do not show striking differences.

\begin{figure}[H]
	\caption{Radar Plot of Sentiment Scores}
	\begin{center}
			\includegraphics[width=0.8\textwidth,keepaspectratio]{../figs/sentscore_radar.png}
			\label{fig_sentscore_radar}
	\end{center}
\end{figure}

@@

\begin{enumerate}
	\item The sentiment value of the SPD is decreasing over time, especially regarding debates within the party (topic 17). 
	\item The topics relating to the coalition talks on Jamaica (26, 27) and the grand coalition (4) are discussed rather critically, but they also show the greatest differences between the media. 
	\item In contrast, the tonality of the topics in relation to the AfD shows rather small differences. 
	\item Overall, the sentiment value at Tagesschau.de is the least negative and only shows a comparatively strong negative value at topic 23, concerning the CSU.
\end{enumerate}

\subsection{News sentiment and poll data}\label{ch_correlation}

@@

In the present paper, the relationship between monthly average of both the sentiment value of individual topics ($x_t$) and the survey value of the parties ($y_t$) is estimated using the cross correlation function (CCF). Thus, the CCF between $x_{t+h}$ and $y_t$ for $h\pm 1$,$h \pm 2$,$h \pm 3$ is computed. A negative value for $h$ is a correlation between the topic sentiment value at a time before $t$ and the survey value at time $t$. The correlation value for $h=0$ indicates the contemporary correlation between the two time series.  Based on the coefficients of the cross correlation estimation shown in Figure \ref{fig_ccf}, the significant correlations between topic sentiment and survey value are evaluated for each party.\footnote{The value of the cross correlation coefficients for lag 0 can be found in the Appendix (Table \ref{apx_corr})} It is important to note that no causal relationships are described below, but that only the correlation between the two time series is described.

The survey results of the AfD correlate negatively with topics relating to the SPD (17, 22) at lag 0. Thus, if the SPD was more negatively reported, the poll value of the AfD increased in the same month (and vice versa). Another significant negative correlation exists between the reporting on the GroKo (4) and the survey value of AfD at lag -1 ($x_{t-1}$). So if the GroKo was more negatively reported in one month, the survey value of the AfD increased in the following month (and vice versa). For the FDP, too, only negative correlation coefficients can be detected, with the strongest negative correlation existing for the topic relating to the CSU (23). If the CSU got off worse in the online news, the poll value of the FDP have gone up. Another interesting observation is that the FDP's poll results correlate negatively with issues relating to the Jamaica coalition at lag 1 ($x_{t+1}$). So if the poll results for the FDP rose in one month, the following month the FDP was reported more negatively. The Green Party survey results show no negative correlation with any of the topics, except topic 30 at lag 1. It is striking that there seems to be a strong negative correlation between the SPD topics (1, 17, 22) and the poll results of the left party (DIE LINKE). This means that the poll value of the left party has climbed if the topics related to the SPD were discussed more negatively. Same applies to the reporting on the GroKo (30) for lag -1. Conversely, the SPD's survey results correlate strongly positively with these topics, and also with topic 30 with a delay of one month. For the CDU/CSU, too, only significant negative correlations are discernible: the survey results correlate negatively with the topic of the Schulz v Merkel debate (10) and negatively with topic 30 with a delay of one month ($x_{t+1}$).

@@

\pagebreak

\printbibliography

\pagebreak

\section*{Appendix}

\subsection*{Most frequent words}\label{apx_tf}
% 1, 2
\begin{figure}[H]
	\begin{center}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote1.png}
		\end{subfigure}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/plotquote2.png}
		\end{subfigure}
	\end{center}
\end{figure}

@@

\subsection*{Regression Results}\label{apx_coeff}
\input{tables/coeff1}
\input{tables/coeff2}

\subsection*{Cross Correlation Coefficient}
\input{tables/corr}
